### 2013-08-20 doc/dissertation/document/frontmatter/acks.tex
adding proper olcf acknowledgement

Thank you to the Oak Ridge Leadership Computing Facility (OLCF) for
providing computational resources and support.

>>>>

This research used resources of the Oak Ridge Leadership Computing
Facility at the Oak Ridge National Laboratory, which is supported by
the Office of Science of the U.S. Department of Energy under Contract
No. DE-AC05-00OR22725.
